---
title: "FIFA"
author: "Jingfei"
date: "3/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(corrplot)
library(car)
library(leaps)
library(ggplot2)
```

```{r}
train <- read.csv('Train_FIFA.csv')
test <- read.csv('Test_FIFA.csv')
```

```{r}
train_num<- train[,sapply(train, is.numeric)]
train_num$Ob <- NULL
cordata <- round(cor(train_num, use = "pairwise.complete.obs"), 4)
#pdf(file = "yourfilename.pdf")
corrplot(cordata, order = "AOE", method = "circle", cl.cex = 0.5, tl.cex=0.5)
#dev.off()
```

```{r}
#scatterplotMatrix(~WageNew + Overall+Potential+Reactions+Composure+BallControl+
             #ShortPassing+Vision+LongShots, data=train)
```



```{r}
mean(train$WageNew[is.na(train$Club)])
mean(train$WageNew[!is.na(train$Club)])
```
# We can see that the mean wage of missing values (of club) is much lower than the mean wage of the other players, so we put all missing valules into a new category.

```{r}
# Club
levels(train$Club) <- c(levels(train$Club), "Non-exist")
train$Club[is.na(train$Club)] <- "Non-exist"
result <- numeric(0)
for(l in levels(train$Club)){
  result <- c(result, with(train, mean(WageNew[Club == l])))
}
names(result) <- levels(train$Club)

# International.Reputation
index <- c("one", "two", "three", "four", "five")
train$International.Reputation <- as.factor(index[train$International.Reputation])
levels(train$International.Reputation) <- c(levels(train$International.Reputation), "Non-exist")
train$International.Reputation[is.na(train$International.Reputation)] <- "Non-exist"
result <- numeric(0)
for(l in levels(train$International.Reputation)){
  result <- c(result, with(train, mean(WageNew[International.Reputation == l])))
}
names(result) <- levels(train$International.Reputation)

#Reactions
na_wage <- mean(train$WageNew[is.na(train$Reactions)])
not_na_wage <- mean(train$WageNew[!is.na(train$Reactions)])

not_na_means <- mean(train$Reactions[!is.na(train$Reactions)])
train$Reactions[is.na(train$Reactions)] <- not_na_means * not_na_wage / na_wage

#Composure
na_wage <- mean(train$WageNew[is.na(train$Composure)])
not_na_wage <- mean(train$WageNew[!is.na(train$Composure)])

not_na_means <- mean(train$Composure[!is.na(train$Composure)])
train$Composure[is.na(train$Composure)] <- not_na_means * not_na_wage / na_wage

#BallControl
na_wage <- mean(train$WageNew[is.na(train$BallControl)])
not_na_wage <- mean(train$WageNew[!is.na(train$BallControl)])

not_na_means <- mean(train$BallControl[!is.na(train$BallControl)])
train$BallControl[is.na(train$BallControl)] <- not_na_means * not_na_wage / na_wage

#ShortPassing
na_wage <- mean(train$WageNew[is.na(train$ShortPassing)])
not_na_wage <- mean(train$WageNew[!is.na(train$ShortPassing)])

not_na_means <- mean(train$ShortPassing[!is.na(train$ShortPassing)])
train$ShortPassing[is.na(train$ShortPassing)] <- not_na_means * not_na_wage / na_wage

#Vision
na_wage <- mean(train$WageNew[is.na(train$Vision)])
not_na_wage <- mean(train$WageNew[!is.na(train$Vision)])

not_na_means <- mean(train$Vision[!is.na(train$Vision)])
train$Vision[is.na(train$Vision)] <- not_na_means * not_na_wage / na_wage

#LongShots
na_wage <- mean(train$WageNew[is.na(train$LongShots)])
not_na_wage <- mean(train$WageNew[!is.na(train$LongShots)])

not_na_means <- mean(train$LongShots[!is.na(train$LongShots)])
train$LongShots[is.na(train$LongShots)] <- not_na_means * not_na_wage / na_wage
```


# Next recode "Club" variable
```{r}
# Club
train$Club[is.na(train$Club)] <- "Non-exist"

result <- numeric(0)

for(l in unique(train$Club)){
  result <- c(result, mean(train[train$Club==l,]$WageNew))
}

result <- setNames(result,unique(train$Club))

result <- sort(result, decreasing = T)

length(result)

hist(result, nclass = 50)

Group1 <- names(result[1:3])

Group2 <- names(result[4:16])

Group3 <- names(result[17:188]
                [result[17:188]>quantile(result[17:188], 0.5)])

Group4 <- names(result[result<=quantile(result[17:188], 0.5)&result>10000])

Group5 <- names(result[result<=10000])

train["Group1"] <- ifelse(train$Club %in% Group1, "Yes", "No")

train["Group2"] <- ifelse(train$Club %in% Group2, "Yes", "No")

train["Group3"] <- ifelse(train$Club %in% Group3, "Yes", "No")

train["Group4"] <- ifelse(train$Club %in% Group4, "Yes", "No")

train["Group5"] <- ifelse(train$Club %in% Group5, "Yes", "No")

train$group <- NA
train[train$Group1 == "Yes", 'group'] <- "Group1"
train[train$Group2 == "Yes", 'group'] <- "Group2"
train[train$Group3 == "Yes", 'group'] <- "Group3"
train[train$Group4 == "Yes", 'group'] <- "Group4"
train[train$Group5 == "Yes", 'group'] <- "Group5"

# train$Group1 <- NULL
# train$Group2 <- NULL
# train$Group3 <- NULL
# train$Group4 <- NULL
# train$Group5 <- NULL
```

 
```{r}
# Club
levels(test$Club) <- c(levels(test$Club), "Non-exist")
test$Club[is.na(test$Club)] <- "Non-exist"
result <- numeric(0)

# International.Reputation
index <- c("one", "two", "three", "four", "five")
test$International.Reputation <- as.factor(index[test$International.Reputation])
levels(test$International.Reputation) <- c(levels(test$International.Reputation), "Non-exist")
test$International.Reputation[is.na(test$International.Reputation)] <- "Non-exist"
result <- numeric(0)

#Reactions
na_wage <- mean(train$WageNew[is.na(test$Reactions)])
not_na_wage <- mean(train$WageNew[!is.na(test$Reactions)])

not_na_means <- mean(test$Reactions[!is.na(test$Reactions)])
test$Reactions[is.na(test$Reactions)] <- not_na_means * not_na_wage / na_wage

#Composure
na_wage <- mean(train$WageNew[is.na(test$Composure)])
not_na_wage <- mean(train$WageNew[!is.na(test$Composure)])

not_na_means <- mean(test$Composure[!is.na(test$Composure)])
test$Composure[is.na(test$Composure)] <- not_na_means * not_na_wage / na_wage

#BallControl
na_wage <- mean(train$WageNew[is.na(test$BallControl)])
not_na_wage <- mean(train$WageNew[!is.na(test$BallControl)])

not_na_means <- mean(test$BallControl[!is.na(test$BallControl)])
test$BallControl[is.na(test$BallControl)] <- not_na_means * not_na_wage / na_wage

#ShortPassing
na_wage <- mean(train$WageNew[is.na(test$ShortPassing)])
not_na_wage <- mean(train$WageNew[!is.na(test$ShortPassing)])

not_na_means <- mean(test$ShortPassing[!is.na(test$ShortPassing)])
test$ShortPassing[is.na(test$ShortPassing)] <- not_na_means * not_na_wage / na_wage

#Vision
na_wage <- mean(train$WageNew[is.na(test$Vision)])
not_na_wage <- mean(train$WageNew[!is.na(test$Vision)])

not_na_means <- mean(test$Vision[!is.na(test$Vision)])
train$Vision[is.na(test$Vision)] <- not_na_means * not_na_wage / na_wage

#LongShots
na_wage <- mean(train$WageNew[is.na(test$LongShots)])
not_na_wage <- mean(train$WageNew[!is.na(test$LongShots)])

not_na_means <- mean(test$LongShots[!is.na(test$LongShots)])
test$LongShots[is.na(test$LongShots)] <- not_na_means * not_na_wage / na_wage
```


# Next recode "Club" variable
```{r}
test["Group1"] <- ifelse(test$Club %in% Group1, "Yes", "No")

test["Group2"] <- ifelse(test$Club %in% Group2, "Yes", "No")

test["Group3"] <- ifelse(test$Club %in% Group3, "Yes", "No")

test["Group4"] <- ifelse(test$Club %in% Group4, "Yes", "No")

test["Group5"] <- ifelse(test$Club %in% Group5, "Yes", "No")

test$group <- NA
test[test$Group1 == "Yes", 'group'] <- "Group1"
test[test$Group2 == "Yes", 'group'] <- "Group2"
test[test$Group3 == "Yes", 'group'] <- "Group3"
test[test$Group4 == "Yes", 'group'] <- "Group4"
test[test$Group5 == "Yes", 'group'] <- "Group5"

# test$Group1 <- NULL
# test$Group2 <- NULL
# test$Group3 <- NULL
# test$Group4 <- NULL
# test$Group5 <- NULL
```

```{r}
lm1 <- lm(WageNew ~ Overall+Potential+Reactions+Composure+BallControl+
             ShortPassing+Vision+LongShots, data = train)
summary(powerTransform(cbind(WageNew, Overall, Potential, Reactions, 
                             Composure, BallControl, ShortPassing, Vision, LongShots) ~ 1, data = train))
```

```{r}
inverseResponsePlot(lm1)
```

```{r}
opt.subset.all <- regsubsets(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + 
                                       I(Reactions^2) + I(Composure^2) +
                                       I(BallControl^2) + I(ShortPassing^2) +
                                        I(Vision^1.5) + LongShots + group + International.Reputation, data =train, method = "exhaustive")
all.model.summary <- summary(opt.subset.all)

all.model.summary
print("adjr2")
coef(opt.subset.all, which.max(all.model.summary$adjr2))
print("bic")
coef(opt.subset.all, which.min(all.model.summary$bic))
```

# suggested by regsubset
```{r}
lm2 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + I(BallControl^2) + 
             I(ShortPassing^2) + group + International.Reputation,
          data = train)
summary(lm2)
vif(lm2)
```

# fixing multicollinearity by removing shortpassing
```{r}
lm3 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + I(BallControl^2) + 
              group + International.Reputation,
          data = train)
vif(lm3)
```

# fixing multicollinearity by removing international.reputation
```{r}
lm4 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + I(BallControl^2) + 
              group,
          data = train)
summary(lm4)
vif(lm4)
par(mfrow = c(2,2))
#plot(lm4)
anova(lm4)
```

# anova suggests ballcontrol is not significant, try removing it
```{r}
lm4_fix <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + 
              group,
          data = train)
anova(lm4_fix, lm4)
summary(lm4_fix)
vif(lm4_fix)
```
# We get a similar R^2 with lm4_fix, so we use lm4_fix.

# Try forwardAIC
```{r}
mint <- lm(log(WageNew)~1, data = train)
forwardAIC <- step(mint, scope = list(lower=~1,
                                     upper=~I(Overall^2.5) + I(Potential^0.75) + 
                                       I(Reactions^2) + I(Composure^2) +
                                       I(BallControl^2) + I(ShortPassing^2) +
                                        I(Vision^1.5) + LongShots + group + 
                                        International.Reputation), direction = "forward", data = train)
```

```{r}
summary(forwardAIC)
vif(forwardAIC)
```


```{r}
mint <- lm(log(WageNew)~1, data = train)
forwardBIC <- step(mint, scope = list(lower=~1,
                                     upper=~I(Overall^2.5) + I(Potential^0.75) + 
                                       I(Reactions^2) + I(Composure^2) +
                                       I(BallControl^2) + I(ShortPassing^2) +
                                        I(Vision^1.5) + LongShots + group + International.Reputation), direction = "forward", data = train, k = log(nrow(train)))
summary(forwardBIC)
vif(forwardBIC)
```

# There's multicollinearity in both forwardAIC and forwardBIC

# BackwardBIC
```{r}
lmnew <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + 
                                       I(Reactions^2) + I(Composure^2) +
                                       I(BallControl^2) + I(ShortPassing^2) +
                                        I(Vision^1.5) + LongShots + group + International.Reputation, data = train)
backBIC <- step(lmnew, direction="backward", data = train, k = log(nrow(train)))

summary(backBIC)
vif(backBIC)
```

# Models suggested by forwardBIC and backwardBIC are the same, and there's multicollinearity.

# fixing multicollinearity by removing Ballcontrol
```{r}
lm5 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + I(Reactions^2) + 
             I(ShortPassing^2) + LongShots + group, data = train)
vif(lm5)
```

# fixing multicollinearity by removing shortpassing
```{r}
lm6 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + I(Reactions^2) + 
              LongShots + group, data = train)
vif(lm6)
anova(lm6)
```

# anova suggests that reactions is not significant, so we try removing it
```{r}
lm7 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + 
              LongShots + group, data = train)
vif(lm7)
anova(lm7)
summary(lm7)
par(mfrow = c(2,2))
plot(lm7)
```

# The diagnostic plots of lm7 look similar to lm4_fix, but it has slightly higher R^2, so we use lm7.

# remove bad leverage points
```{r}
leverage <- hatvalues(lm7)
train <- train[-which(abs(rstandard(lm7)) >= 2 & leverage >= (2 * (7+1)/nrow(train))),]
```

```{r}
lm8 <- lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75) + 
              LongShots + group, data = train)
summary(lm8)
par(mfrow = c(2,2))
plot(lm8)
anova(lm8)
```

# Not much improvement

```{r, warning = FALSE}
mmps(lm(log(WageNew) ~ I(Overall^2.5) + I(Potential^0.75)
              , data = train))
```

```{r}
leveragePlots(lm8)
```

```{r}
lm9 <- lm(log(WageNew) ~ I(Overall^2.5) + 
              I(Potential^0.75) + group, data = train)
summary(lm9)
anova(lm9)
vif(lm9)
par(mfrow = c(2,2))
plot(lm9)
```

# Not much change by removing potential


```{r}
leveragePlots(lm9)
```

```{r}
lm10 <- lm(log(WageNew) ~ I(Overall^2.5) + 
           group, data = train)
summary(lm10)
anova(lm9, lm10)
```

# After removing LongShots, R^2 dropped and partial F-test suggests not removing LongShots, so we keep it.
# Therefore, the final model is lm9!
```{r}
summary(lm9)
vif(lm9)
par(mfrow = c(2,2))
plot(lm9)
```

#actual predict
```{r}
WageNew <- exp(predict(lm9, test))
Ob <- c(1:5462)
sol <- cbind(Ob, WageNew)

write.csv(sol, "sol.csv", row.names = FALSE)
```


Leverage and outlier
```{r}
leverage <- hatvalues(lm9)
bad_leverage_points <- which(abs(rstandard(lm9))>2 & leverage >= 2*(3+1)/nrow(train))
names(bad_leverage_points) <- NULL
bad_leverage_points
```

```{r}
scatterplotMatrix(~I(Overall^2.5) + I(Potential^0.75), data=train)
```

```{r}
data <- data.frame("Potential^0.75" = train$Potential^0.75, "Overall^2.5" = train$Overall^2.5)
cordata <- round(cor(data, use = "pairwise.complete.obs"), 4)
corrplot(cordata, order = "AOE", method = "circle", cl.cex = 0.5, tl.cex=0.5)
```